### 2019-03-27 IEEE_TC_submission.d/intro.tex
ssr

\IEEEPARstart{R}{search} on the symmetry properties of Boolean
functions has received a lot of attention from the
automated logic synthesis community. 
(Additional discussion on this is provided in Section~\ref{sse:related}.)
In this paper, we focus on the symmetry properties of
a class of Boolean functions (called \textbf{nested canalyzing functions})
which are used to model biological phenomena.
To define this class, we start with a simpler
class of functions, called \textbf{canalyzing} Boolean functions.
This class, introduced in \cite{Kauffman-1969}, is defined as follows.

@@

In the literature (see e.g., \cite{Crama-Hammer-2011,HT-2016,Toth-etal-1977}),
a 1-symmetric function $f$ is referred to simply
as a \textbf{symmetric} function.
Thus, in any symmetric function, each pair of variables is symmetric.
As a simple example, the function $f_2(x_1, x_2, x_3)$ = 
$x_1 \oplus x_2 \oplus x_3$ (defined above) is symmetric.
If $f$ is a symmetric function, then for any
input $(a_1, a_2, \ldots, a_n)$ to $f$, where $a_i \in \{0,1\}$ for
$1 \leq i \leq n$, and any permutation $\pi$ of $\{1, 2, \ldots, n\}$,
$f(a_1, a_2, \ldots, a_n)$ = $f(a_{\pi(1)}, a_{\pi(2)}, \ldots, a_{\pi(n)})$.
The class of $r$-symmetric functions have also been
studied in the literature on discrete dynamical systems (see e.g., 
\cite{Barrett-etal-2007,Rosenkrantz-etal-2015,MR-2007}).

@@

Over the years, a considerable amount of research on detecting symmetry properties 
of Boolean functions has been reported in the literature
(e.g., \cite{BS-1968,Biswas-1970,TM-1996,KS-2000,Darga-etal-2008,Maurer-2015}).
Several references have observed the usefulness of detecting symmetries
in automated logic synthesis (e.g., \cite{AP-2008,Hu-etal-2008,Darga-etal-2008}).
Reference \cite{Maurer-2015} provides a thorough discussion of known
symmetry detection algorithms and presents a new universal algorithm 
for detecting any form of permutation-based symmetry in Boolean functions.

>>>>

\IEEEPARstart{R}{search} on the symmetry properties of Boolean
functions has received a lot of attention from the
logic synthesis community. 
(Additional discussion on this is provided in Section~\ref{sse:related}.)
In this paper, we focus on the symmetry properties of
a class of Boolean functions (called \textbf{nested canalyzing functions})
which are used to model biological phenomena.
To define this class, we start with a simpler
class of functions, called \textbf{canalyzing} Boolean functions.
This class, introduced in \cite{Kauffman-1969}, is defined as follows.

@@

In the literature (see e.g., \cite{Crama-Hammer-2011,HT-2016,Toth-etal-1977}),
a 1-symmetric function $f$ is referred to simply
as a \textbf{symmetric} function or 
as a \textbf{totally symmetric function} \cite{Biswas-1970,BS-1968}.
Thus, in any symmetric function, each pair of variables is symmetric.
As a simple example, the function $f_2(x_1, x_2, x_3)$ = 
$x_1 \oplus x_2 \oplus x_3$ (defined above) is symmetric.
If $f$ is a symmetric function, then for any
input $(a_1, a_2, \ldots, a_n)$ to $f$, where $a_i \in \{0,1\}$ for
$1 \leq i \leq n$, and any permutation $\pi$ of $\{1, 2, \ldots, n\}$,
$f(a_1, a_2, \ldots, a_n)$ = $f(a_{\pi(1)}, a_{\pi(2)}, \ldots, a_{\pi(n)})$.
The class of $r$-symmetric functions have also been
studied in the literature on discrete dynamical systems (see e.g., 
\cite{Barrett-etal-2007,Rosenkrantz-etal-2015,MR-2007}).

@@

Over the years, a considerable amount of research on detecting symmetry properties 
of Boolean functions has been reported in the literature.
For example, references \cite{Biswas-1970,TM-1996} present methods 
to determine whether a given Boolean function is symmetric.
Born and Scidmore \cite{BS-1968} show how certain Boolean functions
can be converted into symmetric functions by introducing additional
variables. 
%% (e.g., \cite{BS-1968,Biswas-1970,TM-1996,KS-2000,Darga-etal-2008,Maurer-2015}).
Several references have observed the usefulness of detecting symmetries
in automated logic synthesis (e.g., \cite{AP-2008,Hu-etal-2008,Darga-etal-2008}).
Reference \cite{Maurer-2015} provides a thorough discussion of known
symmetry detection algorithms and presents a new universal algorithm 
for detecting any form of permutation-based symmetry in Boolean functions.
